---
title: "Eating Out"
author: "Wilhelmus Elersich"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE}
GSS <-read.dta(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

### Methods
Because we are only working with categorical variables, we shall use the cat_cat helper file. For graphical results, the barplot shall be used. For numerical results, we shall create a table. Finally, because one of the categorical variables has three categories (white, black, and other) we will use the fisherXY test to determine significance. We do not need to change character variables to factor variables, because the variables we are working with are already factor variables.


### Graphical Results 

```{r}
barchartGC(~race + eatout, data=mydata, type="percent")
```

Here we can see that over 80% of white people who answered this question had eaten out within a week before responding, followed by other people aat just under 80%, and finally by black people at around 75%.

